---
title: "DataChallenge"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1)

```{r}
library(googlesheets4)
library(tidyverse)
```

```{r}
sneakerData <- read.csv('2019WinterDataScienceInternChallengeDataSet-Sheet1.csv')
```

a)

```{r}
summary(sneakerData)
```
Looking at the summary, we can easily see there are outliners for order_amount as there is at least one maximum value of 704000, much higher than the median value of 284, which can skew the average and give us the answer $3145.13. 

```{r}
medSneaker <- median(sneakerData$order_amount)
medSneaker
```

A better way to evaluate the average order value is to remove those outliners before we calculate the average. 

```{r}
outliers <- boxplot(sneakerData$order_amount, plot = FALSE)$out
```

```{r}
sneakerData2 <- sneakerData[!(sneakerData$order_amount %in% outliers), ]
```

```{r}
aov <- mean(sneakerData2$order_amount)
aov
```
As expected, after removing the outliners, we have the new AOV of $293.7154, much closer to the median and more reasonable for sneakers.

b)

For this dataset, I would report the median/average order value, what is the total order/item amount for each shop/payment method.

c)

The median order value is $284.

The average order value after accounting for outliners is $293

The total order/item amount for each shop

```{r}
sneakerData2 %>% group_by(shop_id) %>%
  summarise(totalOrderValue = sum(order_amount),
            totalItemAmount = sum(total_items),
            averageOrderValue = mean(order_amount)
            )
```

```{r}
sneakerData2 %>% group_by(payment_method) %>%
  summarise(totalOrderValue = sum(order_amount),
            totalItemAmount = sum(total_items),
            averageOrderValue = mean(order_amount)
            )
```





